\documentclass{article}
\usepackage{graphicx,fancyhdr,amsmath,amssymb,amsthm,subfig,url,hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{enumerate}
\usepackage{diagbox}

\setlength{\parindent}{0pt}
\def\o{\ensuremath\varnothing}

\graphicspath{{figures/}}
\begin{document}

\section*{Basic}
\textbf{Decision problem: } Answer yes/no

\textbf{P: } Decision problems for which there is a poly-time algorithm.

\textbf{NP: } Decision problems for which there exists a poly-time certifier.
\begin{itemize}
    \item Algorithm $C(s, t)$ is a certifier for problem $X$ if for every string $s$, 
    $s\in X$ iff there exists a string $t$ such that $C(s, t) = \text{yes}$ .
\end{itemize}

\textbf{co-NP: } Complements of decision problems in NP.

\textbf{PSPACE: } Decision problems solvable in polynomial \textbf{space}.

\textbf{EXP: } Decision problems for which there is an exponential-time
algorithm.

\textbf{Claim: } $\text{P} \subseteq \text{NP}, \text{co-NP} \subseteq \text{EXP}$ \qquad
$ \text{NP}\subseteq \text{PSPACE} \subseteq \text{EXP} $

~\\
\textbf{Reduction: }
Problem $X$ \textbf{polynomial-time reduces to} problem $Y$ if arbitrary instances of problem $X$ can be solved using:
\begin{itemize}
    \item Polynomial number of standard computational steps.
    \item Polynomial number of calls to oracle(A black box that solves instances of $Y$ in a single step) that solves problem $Y$.
\end{itemize}
\textbf{Notation: } $X \leq_P Y$.

\noindent
\textbf{Common approach: }
polynomial transformation
\begin{itemize}
    \item Given any input $x$ to $X$, 
    \textbf{construct} an input $y$ in poly-time such that $x$
    is a yes instance of $X$ iff $y$ is a yes instance of $Y$.
\end{itemize}
% other
% \begin{itemize}
%     \item \textbf{Design algorithms:} If $X \leq_P Y$ and $Y$ can be solved in polynomial-time,
%     then $X$ can also be solved in polynomial time.
%     \item \textbf{Establish intractability:} If $X \leq_P Y$ and $X$ cannot be solved in
%     polynomial-time, then $Y$ cannot be solved in polynomial time.
%     \item \textbf{Establish equivalence:} If $X \leq_P Y$ and $Y \leq_P X$, 
%     we use notation $X \equiv_P Y$.
%     In this case, $X$ can be solved in polynomial time iff $Y$ can be.
% \end{itemize}

\section*{NP-Completeness}
\textbf{NP-complete. } 
A problem $Y$ in NP with the property that for every
problem $X$ in NP, $X \leq_P Y$.

Recipe to establish NP-completeness of problem $Y$.
\begin{enumerate}
    \item Show that $Y$ is in NP.
    \item Choose an NP-complete problem $X$.
    \item Prove that $X \leq_P Y$
\end{enumerate}

NPC problem
\begin{itemize}
    \item \textbf{SAT: } Given CNF formula $\Phi$, does it have a satisfying truth assignment.
    \item \textbf{3-SAT: } SAT where each clause contains exactly $3$ literals.
    \item \textbf{INDEPENDENT SET:} Given a graph $G = (V, E)$ and an integer $k$, 
    is there a subset of vertices $S \subseteq V$ such that $|S| \geq k$, 
    and for each edge at most one of its endpoints is in $S$?
    \item \textbf{VERTEX COVER:} Given a graph $G = (V, E)$ and an integer $k$,
    is there a subset of vertices $S \subseteq V$ such that $|S| \leq k$, 
    and for each edge, at least one of its endpoints is in $S$?
    \item \textbf{SET COVER: } Given a set $U$ of elements, 
    a collection $S_1 , S_2 , \cdots , S_m$ of subsets of $U$, 
    and an integer $k$, does there exist a collection of $\leq k$ of
    these sets whose union is equal to $U$?
    \item \textbf{DIR-HAM-CYCLE: } Given a digraph $G = (V, E)$, 
    does there exists a simple directed cycle $\Gamma$ that contains every node in $V$?
    \item \textbf{HAM-CYCLE: } Given an undirected graph $G = (V, E)$, 
    does there exist a simple cycle $C$ that visits every node.
    \item \textbf{TSP: } Given a set of $n$ cities and a pairwise distance function $d(u, v)$, 
    is there a tour of length $\leq D$.
    \item \textbf{GRAPH 3-COLOR: } Given an \textbf{undirected} graph $G$ does there exist a way to color the nodes red, green, and blue so that no adjacent nodes have the same color.
    \item \textbf{3D-MATCHING: } Given disjoint sets $X$, $Y$, and $Z$, 
    each of size $n$ and a set $T \subseteq X \times Y \times Z$ of triples, 
    does there exist a set of $n$ triples in $T$ 
    such that each element of $X \cup Y \cup Z$ is in exactly one of these triples.
    \item \textbf{SUBSET-SUM: } Given natural numbers $w_1 , \cdots, w_n$ and an integer $W$, 
    is there a subset that adds up to exactly $W$.
    \item \textbf{SCHEDULING: } Given a set of $n$ jobs with processing time $t_i$ , 
    release time $r_i$, and deadline $d_i$, 
    is it possible to schedule all jobs on a single machine 
    such that job $i$ is processed with a contiguous slot of $t_i$ time units 
    in the interval $[r_i , d_i ]$
\end{itemize}

\section*{PSPACE-Complete}
Problem $Y$ is PSPACE-complete if (i) $Y$ is in PSPACE
and (ii) for every problem $X$ in PSPACE, $X \leq_P Y$. 

PSPACE-Complete problems
\begin{itemize}
    \item \textbf{QSAT(Quantified 3-SAT)} Let $\Phi(x_1 , \cdots, x_n )$ be a Boolean CNF formula.
    Is the following propositional formula true:
    \begin{equation*}
        \exists x_1 ~\forall x_2 ~\exists x_3 ~\forall x_4\cdots \forall x_{n-1} ~\exists x_n~\Phi(x_1,\cdots, x_n) \qquad n \text{ is odd}
    \end{equation*}
    \item Competitive Facility Location
    \begin{itemize}
        \item \textbf{Input}. Graph with positive node weights, and target number $B$.
        \item \textbf{Game}. Two competing players alternate in selecting nodes. 
        Not allowed to select a node if any of its neighbors has been selected.
        \item \textbf{Competitive facility location}. Can second player guarantee at least $B$
        units of profit?
    \end{itemize}
\end{itemize}

% \section*{Approximation Algorithms}


\section*{Randomized Algorithms}
\begin{itemize}
    \item $(1 - 1/x) x \leq 1/e$\qquad $\ln(n+1)<\sum\limits_{i=1}^n 1/n <1+\ln n $
    \item $(1 - 1/n)^{n}$ converges monotonically from $1/4$ up to $1/e$($n$ increases from $2$)
    \item $(1 - 1/n)^{n-1}$ converges monotonically from $1/2$ down to $1/e$
    \item \textbf{Union bound: } Given events $E_1, \cdots, E_n$, 
    $\text{Pr}[\bigcup\limits_{i=1}^n E_i]\leq \sum\limits_{i=1}^n \text{Pr}[E_i]$
    \item $E[X]=\sum\limits_{j=0}^\infty \text{Pr}[X=j]$
    \item Given two random variables $X$ and $Y$ (not necessarily independent) defined over the same probability space, $E[X + Y] = E[X] + E[Y]$.
\end{itemize}

\textbf{Monte Carlo algorithm: } Guaranteed running time, likely to find correct answer.
\begin{itemize}
    \item Contraction algorithm for global min cut
\end{itemize} 
\textbf{Las Vegas algorithm: } Guaranteed to find correct answer, likely to run in certain time.
\begin{itemize}
    \item Johnson's MAX-3SAT algorithm
    \item Randomized quicksort
\end{itemize}

\end{document}